Language-Based Security for Low-Level MPC

### 2024-07-17 ppdp24/hyper.tex
checkpoint

Since MPC protocols release some information about secrets through
outputs of $\idealf$, they do not enjoy strict noninterference.  As
discussed in Section \ref{section-lang}, public reveals and protocol
outputs are fundamentally forms of declassification.  But consistent
with other work \cite{8429300}, we can formulate a version of
probabilistic noninterference conditioned on output that is sound
for passive security. 
\begin{definition}[Noninterference modulo output]
  \label{definition-NIMO}
  We say that a program $\prog$ with $\iov(\prog) = S \cup V \cup O$
  satisfies \emph{noninterference modulo output}
  iff for all $H$ and $C$ and $\store_1 \in \mems(S_C \cup O)$ and $\store_2 \in \mems(\houtputs)$
  we have:
  $$
  \condd{\progtt(\prog)}{S_H}{\store_1} = \condd{\progtt(\prog)}{S_H}{\store_1 \uplus \store_2}
 $$
\end{definition}
%\begin{definition}[Noninterference modulo output]
%  \label{definition-NIMO}
%  We say that a program $\prog$ satisfies \emph{noninterference modulo output}
%  iff for all $H$ and $C$ and 
%  $\store_1,\store_2 \in \mems(S)$ we have:
%  $$
%  (\store_1 =_C \store_2 \ \wedge \ 
%  (\condd{\progtt(\prog)}{O}{\store_1} = \condd{\progtt(\prog)}{O}{\store_2}))
%  \implies 
%  (\condd{\progtt(\prog)}{\houtputs}{\store_1} = \condd{\progtt(\prog)}{\houtputs}{\store_2})
%  $$
%  where $\iov(\prog) = S \cup V \cup O$.
%\end{definition}
This conditional noninterference property implies that
corrupt views give the adversary no better chance of guessing honest
secrets than just the output and corrupt inputs do. So the simulator
can just arbitrarily pick any honest secrets that could have produced
the given outputs and run the protocol in simulation to reconstruct
real world corrupt views. This requires that the simulator can
tractably ``pre-image'' a given output of a functionality $\idealf$,
to determine the inputs that could have produced it. This equivalence
class is called a \emph{kernel} in recent work \cite{10.1145/3571740}.
\begin{definition}
  Given a functionality $\idealf$ and outputs $\store_{\mathit{out}}$, their 
  \emph{kernel}, denoted $\ik(\idealf,\store_{\mathit{out}})$ is
  $
  \{ \store\ |\ \idealf(\store) = \store_{\mathit{out}} \}
  $.
  We say that $\idealf$ is \emph{pre-imageable} iff $\ik(\idealf, \store_{\mathit{out}})$ for all
  $\store_{\mathit{out}}$ can be computed tractably.
\end{definition}
A soundness result for passive security can then be given as follows.
It is essentially the same as ``perfect passive NI security'' explored
in previous work \cite{8429300}.  
\begin{restatable}{theorem}{nimosecure}
  \label{theorem-nimo}
  Assume given pre-imageable $\idealf$ and a protocol $\prog$ that
  correctly implements $\idealf$.  If $\prog$ satisfies noninterference modulo output
  then $\prog$ is passive secure.
\end{restatable}

@@

Probabilistic noninterference is related to perfect secrecy and is
preserved by components of cryptographic protocols generally. It can
be expressed using probabilistic independence, aka separation,
\cite{darais2019language,barthe2019probabilistic}, and we adopt the
following notation to express independence:
\begin{definition}
%  We write $\vc{\pmf}{x}{y}$ iff $\pmf(\{ x \mapsto 0\}\ |\ \{ y \mapsto 0 \}) =
%  \pmf(\{ x \mapsto 1\}\ |\ \{ y \mapsto 1 \}) = 1$.
  We write $\sep{\pmf}{X}{Y}$ iff for all
    $\store \in \mems(X \cup Y)$ we have
  $\margd{\pmf}{X \cup Y}(\store) =
  \pmf(\store_X) * \pmf(\store_Y)$
\end{definition}

@@

\begin{proof}
  Let $\prog$ be some protocol with passive security and integrity
  where $\iov(\prog) = S \cup V \cup O$, and let $\adversary$ be some
  adversary. Suppose $\store \in \aruns(\prog,\adversary)$.
  As integrity requires, and as Lemma \ref{lemma-malicious-correct}
  demonstrates with respect to outputs, the most the adversary can do
  in the presence of integrity is to elicit the same responses from
  the honest parties-- via the strategy $\store_{\cinputs}$-- as
  are elicited from some passive run of the protocol using
  some $\store' \in \mems(S)$ where $\store'_H = \store_{S_H}$,
  and perhaps to force an abort after some number of message
  exchanges.

  Therefore, in simulation, $\adversary$ can provide the simulator
  with some $\store'_C$ in $\SIM_1$ which its strategy is ``impersonating'',
  allowing $\idealf(\store')$ to
  be communicated to $\adversary$ in $\SIM_2$ who can then
  decide whether or not to abort. In the case of abort, the
  subset of $\houtputs$ to be defined can be communicated to
  $\SIM_3$, along with $\idealf(\store')$, via $\Sigma$. 
  In $\SIM_3$, the simulator can then run $\prog$ in simulation
  with inputs $\store'_C$ and arbitrary $\store'' \in \mems(S_H)$
  such that $\store'_C \uplus \store'' \in \ik(\idealf,\idealf(\store'))$.
  The assumption of passive security of $\prog$ implies the result.
\end{proof}

>>>>

Since MPC protocols release some information about secrets through
outputs of $\idealf$, they do not enjoy strict noninterference.  As
discussed in Section \ref{section-lang}, public reveals and protocol
outputs are fundamentally forms of declassification.  But consistent
with other work \cite{8429300}, we can formulate a version of
probabilistic noninterference conditioned on output that is sound
for passive security. 
\begin{definition}[Noninterference modulo output]
  \label{definition-NIMO}
  We say that a program $\prog$ with $\iov(\prog) = S \cup V \cup O$
  satisfies \emph{noninterference modulo output}
  iff for all $H$ and $C$ and $\store_1 \in \mems(S_C \cup O)$ and $\store_2 \in \mems(\houtputs)$
  we have:
  $$
  \condd{\progtt(\prog)}{S_H}{\store_1} = \condd{\progtt(\prog)}{S_H}{\store_1 \uplus \store_2}
 $$
\end{definition}
%\begin{definition}[Noninterference modulo output]
%  \label{definition-NIMO}
%  We say that a program $\prog$ satisfies \emph{noninterference modulo output}
%  iff for all $H$ and $C$ and 
%  $\store_1,\store_2 \in \mems(S)$ we have:
%  $$
%  (\store_1 =_C \store_2 \ \wedge \ 
%  (\condd{\progtt(\prog)}{O}{\store_1} = \condd{\progtt(\prog)}{O}{\store_2}))
%  \implies 
%  (\condd{\progtt(\prog)}{\houtputs}{\store_1} = \condd{\progtt(\prog)}{\houtputs}{\store_2})
%  $$
%  where $\iov(\prog) = S \cup V \cup O$.
%\end{definition}
This conditional noninterference property implies that
corrupt views give the adversary no better chance of guessing honest
secrets than just the output and corrupt inputs do. So the simulator
can just arbitrarily pick any honest secrets that could have produced
the given outputs and run the protocol in simulation to reconstruct
real world corrupt views. This requires that the simulator can
tractably ``pre-image'' a given output of a functionality $\idealf$,
to determine the inputs that could have produced it. This equivalence
class is called a \emph{kernel} in recent work \cite{10.1145/3571740}.
\begin{definition}
  Given a functionality $\idealf$ and outputs $\store_{\mathit{out}}$, their 
  \emph{kernel}, denoted $\kernel{\idealf}{\store_{\mathit{out}}}$ is
  $
  \{ \store\ |\ \idealf(\store) = \store_{\mathit{out}} \}
  $.
  We say that $\idealf$ is \emph{pre-imageable} iff $\kernel{\idealf}{\store_{\mathit{out}}}$ for all
  $\store_{\mathit{out}}$ can be computed tractably.
\end{definition}
A soundness result for passive security can then be given as follows.
It is essentially the same as ``perfect passive NI security'' explored
in previous work \cite{8429300}.  
\begin{restatable}{theorem}{nimosecure}
  \label{theorem-nimo}
  Assume given pre-imageable $\idealf$ and a protocol $\prog$ that
  correctly implements $\idealf$.  If $\prog$ satisfies noninterference modulo output
  then $\prog$ is passive secure.
\end{restatable}

@@

Probabilistic noninterference is related to perfect secrecy and is
preserved by components of cryptographic protocols generally. It can
be expressed using probabilistic independence, aka separation,
\cite{darais2019language,barthe2019probabilistic}, and we adopt the
following notation to express independence:
\begin{definition}
%  We write $\vc{\pmf}{x}{y}$ iff $\pmf(\{ x \mapsto 0\}\ |\ \{ y \mapsto 0 \}) =
%  \pmf(\{ x \mapsto 1\}\ |\ \{ y \mapsto 1 \}) = 1$.
  We write $\sep{\pmf}{X_1}{X_2}$ iff for all
    $\store \in \mems(X_1 \cup X_2)$ we have
  $\margd{\pmf}{X_1 \cup X_2}(\store) =
  \pmf(\store_{X_1}) * \pmf(\store_{X_2})$
\end{definition}

@@

\begin{proof}
  Let $\prog$ be some protocol with passive security and integrity
  where $\iov(\prog) = S \cup V \cup O$, and let $\adversary$ be some
  adversary. Suppose $\store \in \aruns(\prog)$.
  As integrity requires, and as Lemma \ref{lemma-malicious-correct}
  demonstrates with respect to outputs, the most the adversary can do
  in the presence of integrity is to elicit the same responses from
  the honest parties-- via the strategy $\store_{\cinputs}$-- as
  are elicited from some passive run of the protocol using
  some $\store' \in \mems(S)$ where $\store'_H = \store_{S_H}$,
  and perhaps to force an abort after some number of message
  exchanges.

  Therefore, in simulation, $\adversary$ can provide the simulator
  with some $\store'_C$ in $\SIM_1$ which its strategy is ``impersonating'',
  allowing $\idealf(\store')$ to
  be communicated to $\adversary$ in $\SIM_2$ who can then
  decide whether or not to abort. In the case of abort, the
  subset of $\houtputs$ to be defined can be communicated to
  $\SIM_3$, along with $\idealf(\store')$, via $\Sigma$. 
  In $\SIM_3$, the simulator can then run $\prog$ in simulation
  with inputs $\store'_C$ and arbitrary $\store'' \in \mems(S_H)$
  such that $\store'_C \uplus \store'' \in \kernel{\idealf}{\idealf(\store')}$.
  The assumption of passive security of $\prog$ implies the result.
\end{proof}
